Predicting sales of newly published books

### 2015-08-18 paper.tex
traducidos los nombres de variables en el .tex

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.

@@

%Sales forecasting in editorial industry is a very complex problem. 
        %hala, vuelta la burra al trigo - JJ
        %[Pedro] ea, lo quito
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.

@@

  %[Pedro] me falta poner ya los nombres traducidos (y usarlos para los SOM)

@@

\begin{minipage}{2.3in} \begin{verbatim}
devolucion_total
reimpresiones
puntos_vta1anio_total
ejemplares_distribuidos_en_novedad
numero_reimpresiones
devolucion1anio_total
colocado1anio_total
puntos_vta_total
semanas_venta
colocado_total
pvp
tirada
venta_total (output)
\end{verbatim} \end{minipage}     \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
ejemplares_distribuidos_en_novedad
puntos_vta_total
colocado_total
pvp
materia
editorial
venta_total (output)
\end{verbatim} \end{minipage}     \\

>>>>

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales forecasting 
is proposed to solve three real-world sales forecasting problems involving new tea, 
cosmetic, and soft drink products taking into account quantitative variables. 
In this study, it is assumed that products are classified based on their sales 
pattern so that products in the same class would have similar sales pattern.
However, as the authors state, proposed system can not deal with qualitative 
date related to the products, and even more real-world cases, such as consumer 
electronics and fashion products, should be examined, as these industries 
introduce new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where there is historical data available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.

@@

%Sales forecasting in editorial industry is a very complex problem. 
        %hala, vuelta la burra al trigo - JJ
        %[Pedro] ea, lo quito   :)
There are several difficulties inherent to the new book sales forecasting, such as dealing with limited data, finding adequate forecasting methods, and selecting the best method to use \cite{ChingChin2010}.

@@

@@

\begin{minipage}{2.3in} \begin{verbatim}
TOTAL DEVOLUTIONS
REPRINTS
TOTAL SELLING POINTS FIRST YEAR
UNITS DISTRIBUTED IN FIRST EDITION
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS FIRT YEAR
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
WEEKS ON SALE
TOTAL DISTRIBUTED
RETAIL PRICE
PRINT-RUN
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
TOTAL DISTRIBUTED
RETAIL PRICE
SUBJECT-MATTER
EDITORIAL
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\
